\textbf{Best practices for applying machine learning to bacterial 16S rRNA gene sequencing data}

### 2019-07-22 submission/manuscript.tex
update manuscript for Pat

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{caption}
\usepackage{makecell}
\usepackage{threeparttable}

@@

Moreover, there is a lack of discussion on why a particular ML model is
utilized and a lack of emphasis on the strengths and weaknesses of it.
Recently, there is a trend towards using more complex ML models such as
random forest, extreme gradient boosting (XGBoost) and neural networks
without a discussion on if and how much model interpretibility is
necessary for the study (11, 21--23). These models are also called black
box ML models because they are not inherently interpretable and require
posthoc explanations to determine the feature importances in making a
prediction. These explanations can be misleading and at times unreliable
when making high-stake decisions about patient health (24). The models
we develop for healthcare, both to predict disease and to understand
underlying reasons behind that prediction, should be transparent and
accountable (25).

@@

To highlight the differences between the two interpretation methods, we
used permutation importance to interpret linear models as well {[}Figure
S3{]}. L1-regularized SVM with linear kernel picked out some of the same
OTUs (OTU00822, OTU01239, OTU00609) as important in feature rankings
based on weights {[}Figure 3{]} and permutation importance {[}Figure
S3{]}. Similarly, L2-regularized SVM and L2-regularized logistic
regression picked out some of the same OTUs in both interpretation
methods, OTU00659 and OTU00012, respectively. However, for all the
linear models, the rankings of these features were different due to the
collinearity in microbial communities.

@@

We compared the training times of the seven ML models. As the complexity
of a ML model {[}Table S1{]} and the number of tuned hyperparameter
settings increased {[}Figures S1-S2{]}, its training times increased as
well {[}Figure 5{]}. Linear models trained faster than non-linear
models. L1 and L2 SVM with linear kernel and L2-regularized logistic
regression had the shortest training times with 0.2 hours, (std ± 0.03),
0.2 hours, (std ± 0.02), and 0.2 hours, (std ± 0.02), respectively.
Whereas, a decision tree, SVM with radial basis function kernel, random
forest and XGBoost had training times of 4.4 hours, (std ± 0.3), 59.6
hours, (std ± 8.8), 83.2 hours, (std ± 11.3) and 155.1 hours, (std ± 1),
respectively {[}Figure 5{]}.

@@

In this study we established a rigorous ML pipeline to use 16S rRNA
sequence counts to predict a binary health outcome. We built on others'
work in the microbiome field to set-up standards for developing and
evaluating ML models for microbiome data (28--30). First, we used a
held-out test set to illustrate the difference between cross-validation
and testing AUROC values. When the difference between cross-validation
and test performance is low, this suggest the models are not overfit and
that they will perform similar with similar data. In all seven models,
the difference between median cross-validation and testing AUROC values
did not exceed 0.021 which suggests that these models are generalizable
and can be used to test similar new data. Second, we performed the
initial 80\%-20\% random datasplit 100 times in our ML pipeline. The
randomization of the initial data-split to create a held-out test set is
a crucial step in the ML pipeline to develop robust ML models and to
report reliable performance metrics. Depending on how the data is split,
there is the chance of being overoptimistic about the predictive
performance of a model. In our study, we showed that there was
variability in AUROC values between different random data-splits in each
of the models we tested. Our results showed that the testing AUROC
values varied 0.23 on average between different data-splits. Third, we
used the AUROC metric in our study to evaluate the predictive
performance of the ML models. AUROC is always random at the value 0.5
and is a robust metric when a dataset is imbalanced. We also performed a
full grid search for hyperparameter settings when building a ML model.
Default hyperparameter settings in previously developed ML packages in
R, Python, and Matlab programming languages are inadequate for effective
application of classification algorithms and need to be optimized for
each new dataset used to generate a model. In the example of
L1-regularized SVM with linear kernel {[}Figure S1{]}, the model showed
large variability between different regularization coefficients (C) and
was susceptible to performing poorly if the wrong regularization
coefficient was assigned to the model by default.

In this study, we benchmarked seven ML models with different
classification algorithms to show that we should use ML models based on
the goal of the study and our expectations of predictive performance,
interpretability and computational burden. Microbiome studies use ML
models with a classification task to learn the training data to assign
labels, such as healthy or not to new data, but also to learn which
features are important to discriminate between labels (2--11). Our
results show that if the goal of a study is to learn the ecology behind
a disease and to identify microbial biomarkers, we could create ML
models that are inherently interpretable without losing predictive
power. In terms of predictive performance, random forest model had the
best testing AUROC values compared to the other 6 models. However, the
second best model was L2-regularized logistic regression with a median
AUROC difference of only 0.015 compared to random forest. In terms of
interpretability, random forest was a complex ML model and could only be
explained using methods such as permutation importance. On the other
hand, L2-regularized logistic regression was easier to interpret
(i.e.~ranking absolute regression coefficients of the trained model).

Even with interpretable models such as L2-regularized logistic
regression, we need to be careful with how we treat the information we
get from the models. In this study we used two different methods to
interpret our linear models; ranking each OTU by (1) their absolute
weights in the trained models and (2) their impact on the predictive
performance based on permutation importance. We observed differences in
the OTU rankings between the two interpretation methods due to
collinearity in the dataset. Collinearity in a microbial dataset is when
one OTU is highly correlated with another OTU which causes feature
weights to not be unique. The feature weights of correlated OTUs are
influenced by one another which makes it difficult to interpret the ML
model. To avoid misinterpreting the models we should use the highly
ranked correlated OTUs to generate hypotheses about the ecology of the
disease and test them with follow-up experiments.

There are other criteria when choosing ML models such as the
computational burden of developing it and the sample size. In terms of
computational burden, random forest model trained each data-split in
83.2 hours whereas L2-regularized logistic regression trained in 12
minutes. The generalization performance of ML models depends on sample
size. The more complex the model, the more data it will need. The
dataset we used for our study had 490 samples, however microbiome
studies that have smaller sample sizes would benefit from using less
complex models such as L2-regularized logistic regression.

This study highlights the need to make educated choices at every step of
developing a ML model with microbiome data. Model selection should be
done with a solid understanding of model complexity and
interpretability, rigorous ML pipelines should be built with
cross-validation for hyperparameter tuning and with a held-out test set
for evaluating predictive performance and models should be interpreted
while considering collinearity in datasets. The right methods will help
us achieve the level of validity and accountability we want from models
built for patient health.

@@

\textbf{Data collection and study population.} The data used for this
analysis are stool bacterial abundances and clinical information of the
patients recruited by Great Lakes-New England Early Detection Research
Network study. These data were obtained from Sze et al (31). The stool
samples were provided by recruited adult participants who were
undergoing scheduled screening or surveillance colonoscopy.
Colonoscopies were performed and fecal samples were collected from
participants in four locations: Toronto (ON, Canada), Boston (MA, USA),
Houston (TX, USA), and Ann Arbor (MI, USA). Patients' colonic health was
labeled by colonoscopy with adequate preparation and tissue
histopathology of all resected lesions. Patients with an adenoma greater
than 1 cm, more than three adenomas of any size, or an adenoma with
villous histology were classified as advanced adenoma. Study had 172
patients with normal colonoscopies, 198 with adenomas and 120 with
carcinomas. Of the 198 adenomas, 109 were identified as advanced
adenomas. Stool provided by the patients was used for 16S rRNA gene
sequencing to measure bacterial population abundances. The bacterial
abundance data was generated by Sze et al, by processing 16S rRNA
sequences in Mothur (v1.39.3) using the default quality filtering
methods, identifying and removing chimeric sequences using VSEARCH and
assigning to OTUs at 97\% similarity using the OptiClust algorithm
(32--34).

@@

For L2-regularized logistic regression, L1 and L2 support vector
machines (SVM) with linear and radial basis function kernels we tuned
the \textbf{cost} hyperparameter which determines the regularization
strength where smaller values specify stronger regularization. For SVM
with radial basis function kernel we also tuned \textbf{sigma}
hyperparameter which determines the reach of a single training instance
where for a high value of sigma, the SVM decision boundary will be
dependent on the points that are closest to the decision boundary. For
the decision tree model, we tuned the \textbf{depth of the tree} where
deeper the tree, the more splits it has. For random forest, we tuned the
\textbf{number of features} to consider when looking for the best tree
split. For XGBoost, we tuned for \textbf{learning rate} and the
\textbf{fraction of samples} to be used for fitting the individual base
learners.For hyperparameter selection, we started with a granular grid
search. Then we narrowed and fine-tuned the range of each
hyperparameter. The range of the grid depends on the ML task and ML
model. A full grid search needs to be performed to avoid variability in
testing performance. We can use hyper-band to help us with our
hyperparameter selection (35).

@@

\hypertarget{ref-sze_leveraging_2018}{}
31. \textbf{Sze MA}, \textbf{Schloss PD}. 2018. Leveraging existing 16S
rRNA gene surveys to identify reproducible biomarkers in individuals
with colorectal tumors. mBio \textbf{9}:e00630--18.
doi:\href{https://doi.org/10.1128/mBio.00630-18}{10.1128/mBio.00630-18}.

\hypertarget{ref-schloss_introducing_2009}{}
32. \textbf{Schloss PD}, \textbf{Westcott SL}, \textbf{Ryabin T},
\textbf{Hall JR}, \textbf{Hartmann M}, \textbf{Hollister EB},
\textbf{Lesniewski RA}, \textbf{Oakley BB}, \textbf{Parks DH},
\textbf{Robinson CJ}, \textbf{Sahl JW}, \textbf{Stres B},
\textbf{Thallinger GG}, \textbf{Van Horn DJ}, \textbf{Weber CF}. 2009.
Introducing mothur: Open-Source, Platform-Independent,
Community-Supported Software for Describing and Comparing Microbial
Communities. ApplEnvironMicrobiol \textbf{75}:7537--7541.

\hypertarget{ref-westcott_opticlust_2017}{}
33. \textbf{Westcott SL}, \textbf{Schloss PD}. 2017. OptiClust, an
Improved Method for Assigning Amplicon-Based Sequence Data to
Operational Taxonomic Units. mSphere \textbf{2}.
doi:\href{https://doi.org/10.1128/mSphereDirect.00073-17}{10.1128/mSphereDirect.00073-17}.

\hypertarget{ref-rognes_vsearch_2016}{}
34. \textbf{Rognes T}, \textbf{Flouri T}, \textbf{Nichols B},
\textbf{Quince C}, \textbf{Mahé F}. 2016. VSEARCH: A versatile open
source tool for metagenomics. PeerJ \textbf{4}:e2584.
doi:\href{https://doi.org/10.7717/peerj.2584}{10.7717/peerj.2584}.

\hypertarget{ref-li_hyperband:_2016}{}
35. \textbf{Li L}, \textbf{Jamieson K}, \textbf{DeSalvo G},
\textbf{Rostamizadeh A}, \textbf{Talwalkar A}. 2016. Hyperband: A novel
bandit-based approach to hyperparameter optimization. arXiv:160306560
{[}cs, stat{]}.

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{caption}

@@

Moreover, there is a lack of discussion on why a particular ML model is
utilized and a lack of emphasis on the strengths and weaknesses of it.
Recently, there is a trend towards using more complex ML models such as
random forest, extreme gradient boosting (XGBoost) and neural networks
without a discussion on if and how much model interpretability is
necessary for the study (11, 21--23). These models are also called black
box ML models because they are not inherently interpretable and require
posthoc explanations to determine the feature importances in making a
prediction. These explanations can be misleading and at times unreliable
when making high-stake decisions about patient health (24). The models
we develop for healthcare, both to predict disease and to understand
underlying reasons behind that prediction, should be transparent and
accountable (25).

@@

To highlight the differences between the two interpretation methods, we
used permutation importance to interpret linear models as well {[}Figure
S3{]}. L1-regularized SVM with linear kernel picked out some of the same
OTUs (OTU00822, OTU01239, OTU00609) as important in feature rankings
based on weights {[}Figure 3{]} and permutation importance {[}Figure
S3{]}. Similarly, L2-regularized SVM and L2-regularized logistic
regression picked out some of the same OTUs in both interpretation
methods, OTU00659 and OTU00012, respectively. However, for all the
linear models, the rankings of these features were different due to the
collinearity in microbial communities. Collinearity in a microbial
dataset is when one OTU is dependant on another OTU. The feature weights
of correlated OTUs are influenced by one another which makes it
difficult to interpret models using feature weights. Our interpretation
of L2-regularized logistic regression based on feature weight rankings,
showed that an OTU that belongs to \emph{Lachnospiraceae} (OTU00056) was
not among the most important OTUs in making a prediction {[}Figure
3C{]}. However, it was picked out as important when the same model was
interpreted using permutation importance {[}Figure S3C{]}. This is due
to collinearity in the dataset, where \emph{Lachnospiraceae} (OTU00056)
is significantly correlated with \emph{Feacalibacterium} (OTU00015)
which has the highest ranked feature weights {[}Figure 3C{]}. We need to
investigate the relationships among features to identify the true
underlying factors when making a prediction.

@@

We compared the training times of the seven ML models. As the complexity
of a ML model and the number of tuned hyperparameter settings increased
{[}Figures S1-S2{]}, its training times increased as well {[}Figure
5{]}. Linear models trained faster than non-linear models. L1 and
L2-regularized SVM with linear kernel and L2-regularized logistic
regression had the shortest training times with 0.2 hours, (std ± 0.03),
0.2 hours, (std ± 0.02), and 0.2 hours, (std ± 0.02), respectively.
Whereas, a decision tree, SVM with radial basis function kernel, random
forest and XGBoost had training times of 4.4 hours, (std ± 0.3), 59.6
hours, (std ± 8.8), 83.2 hours, (std ± 11.3) and 155.1 hours, (std ± 1),
respectively {[}Figure 5{]}.

@@

Microbiome studies use ML models, often with a classification task, to
predict a disease but also to learn which microbes are indicators of
that disease (2--11). Achieving either of these tasks have far-reaching
impact on human health, however ML as a tool in microbiome studies is
still at its infancy. A framework is needed to develop rigorous ML
models, to identify and overcome potential pitfalls. Previous studies
generated workflows to allow ML to be widely used by the microbiome
researchers (28--31). This study sets-up standards for developing and
evaluating rigorous ML models for microbiome data {[}Table 1{]}.

We benchmarked seven ML models with different classification algorithms
to show that a clearly defined ML problem that is based on the goal of
the microbiome study should inform our model selection. Our results
showed that if the goal of a study is to learn the ecology behind a
disease and to identify microbial biomarkers, we can create ML models
that are inherently interpretable and easily trained without losing
predictive power. In terms of predictive performance, random forest
model had the best testing AUROC values compared to the other six
models. However, the second best model was L2-regularized logistic
regression with a median AUROC difference of only 0.015 compared to
random forest. While random forest took 83.2 hours to train,
L2-regularized logistic regression trained in 12 minutes. In terms of
interpretability, random forest was a more complex ML model and could
only be explained using methods such as permutation importance. On the
other hand, L2-regularized logistic regression was easier to interpret
by ranking absolute feature weights of the trained model.

Even with interpretable models such as L2-regularized logistic
regression, there are potential pitfalls when it comes to identifying
biomarkers of a disease. As domain experts, we know that
human-associated microbial communities have complex correlation
structures that creates collinearity in the dataset. Collinearity is a
severe problem and needs to be addressed to reliably interpret ML models
(32). In this study we used two different methods to interpret our
linear models; ranking each OTU by (1) their absolute weights in the
trained models and (2) their impact on the predictive performance based
on permutation importance. We observed differences in the OTU rankings
between the two interpretation methods due to collinearity in the
dataset. To avoid misinterpreting the models, once we identify the most
important microbes, we should check for their relationships with other
microbes as well. These relationships will help us generate new
hypotheses about the ecology of the disease. These hypotheses needs to
be tested with follow-up experiments to identify the true biomarkers of
a disease.

In this study, we also established a rigorous ML pipeline to use 16S
rRNA sequence counts to predict a binary health outcome. First of all,
we used a held-out test set to illustrate the difference between
cross-validation and testing AUROC values. When the difference between
cross-validation and test performance is low, this suggest the models
are not overfit and that they will perform similar with similar data. In
all the models, the difference between median cross-validation and
testing AUROC values did not exceed 0.021 which suggests that these
models are generalizable and can be used to test similar new data.
Furthermore, we performed the initial 80\%-20\% random datasplit 100
times in our ML pipeline. Depending on how the data is split, there is
the chance of being overoptimistic about the predictive performance of a
model. We showed that there was variability in AUROC values between
different random data-splits in each of the models we tested. Our
results showed that the testing AUROC values varied 0.23 on average
between different data-splits. The randomization and resampling of the
initial data-split to create a held-out test set is a crucial step in
the ML pipeline to develop robust ML models and to report reliable
performance metrics. We also performed a full grid search for
hyperparameter settings when training our ML models. Default
hyperparameter settings in previously developed ML packages in R,
Python, and Matlab programming languages are inadequate for effective
application of classification algorithms and need to be optimized for
each new dataset used to generate a model. In the example of
L1-regularized SVM with linear kernel {[}Figure S1{]}, the model showed
large variability between different regularization coefficients (C) and
was susceptible to performing poorly if the wrong regularization
coefficient was assigned to the model by default. And finally, we used
the AUROC metric in our study to evaluate the predictive performance of
the ML models. AUROC is always random at the value 0.5 and is a robust
metric when a dataset is imbalanced.

We used a balanced CRC dataset to develop ML models with a binary
classification task. We did not evaluate multicategory classification
methods or regression analyses to predict non-binary outcomes. However,
the principles highlighted throughout this study {[}Table 1{]} apply to
all ML modeling tasks with microbiome data. The models we built were
generalizable despite the high number of features microbiome datasets
usually have. The generalization performance of ML models depends on
sample size. The more complex the model, the more data it will need. Our
dataset had 490 samples, however microbiome studies that have smaller
sample sizes would benefit from using less complex models. Our analysis
was limited to shallow learning methods and did not explore deep
learning methods such as neural networks. Microbiome datasets often
suffer from having high dimensionality but low sample sizes which makes
deep learning models prone to overfitting. There are studies that
address overcoming these challenges in biomedical datasets (11, 33, 34),
however sudies that estalish frameworks with microbiome data are
lacking. This would be an interesting direction for future work in
microbiome studies.

This study highlighted the need to make educated choices at every step
of developing a ML model with microbiome data. Model selection should be
done with a solid understanding of model complexity and
interpretability, rigorous ML pipelines should be built with
cross-validation for hyperparameter tuning and with a held-out test set
for evaluating predictive performance and models should be interpreted
while considering collinearity in datasets. The right methods will help
us achieve the level of validity and accountability we want from models
built for patient health.

@@

\textbf{Data collection and study population.} The data used for this
analysis are stool bacterial abundances and clinical information of the
patients recruited by Great Lakes-New England Early Detection Research
Network study. These data were obtained from Sze et al (35). The stool
samples were provided by recruited adult participants who were
undergoing scheduled screening or surveillance colonoscopy.
Colonoscopies were performed and fecal samples were collected from
participants in four locations: Toronto (ON, Canada), Boston (MA, USA),
Houston (TX, USA), and Ann Arbor (MI, USA). Patients' colonic health was
labeled by colonoscopy with adequate preparation and tissue
histopathology of all resected lesions. Patients with an adenoma greater
than 1 cm, more than three adenomas of any size, or an adenoma with
villous histology were classified as advanced adenoma. Study had 172
patients with normal colonoscopies, 198 with adenomas and 120 with
carcinomas. Of the 198 adenomas, 109 were identified as advanced
adenomas. Stool provided by the patients was used for 16S rRNA gene
sequencing to measure bacterial population abundances. The bacterial
abundance data was generated by Sze et al, by processing 16S rRNA
sequences in Mothur (v1.39.3) using the default quality filtering
methods, identifying and removing chimeric sequences using VSEARCH and
assigning to OTUs at 97\% similarity using the OptiClust algorithm
(36--38).

@@

For L2-regularized logistic regression, L1 and L2 support vector
machines (SVM) with linear and radial basis function kernels we tuned
the \textbf{cost} hyperparameter which determines the regularization
strength where smaller values specify stronger regularization. For SVM
with radial basis function kernel we also tuned \textbf{sigma}
hyperparameter which determines the reach of a single training instance
where for a high value of sigma, the SVM decision boundary will be
dependent on the points that are closest to the decision boundary. For
the decision tree model, we tuned the \textbf{depth of the tree} where
deeper the tree, the more splits it has. For random forest, we tuned the
\textbf{number of features} to consider when looking for the best tree
split. For XGBoost, we tuned for \textbf{learning rate} and the
\textbf{fraction of samples} to be used for fitting the individual base
learners.For hyperparameter selection, we started with a granular grid
search. Then we narrowed and fine-tuned the range of each
hyperparameter. The range of the grid depends on the ML task and ML
model. A full grid search needs to be performed to avoid variability in
testing performance. We can use hyper-band to help us with our
hyperparameter selection (39).

@@

\hypertarget{ref-vangay_microbiome_2019}{}
31. \textbf{Vangay P}, \textbf{Hillmann BM}, \textbf{Knights D}. 2019.
Microbiome learning repo (ML repo): A public repository of microbiome
regression and classification tasks. Gigascience \textbf{8}.
doi:\href{https://doi.org/10.1093/gigascience/giz042}{10.1093/gigascience/giz042}.

\hypertarget{ref-dormann_collinearity:_2013}{}
32. \textbf{Dormann CF}, \textbf{Elith J}, \textbf{Bacher S},
\textbf{Buchmann C}, \textbf{Carl G}, \textbf{Carré G}, \textbf{Marquéz
JRG}, \textbf{Gruber B}, \textbf{Lafourcade B}, \textbf{Leitão PJ},
\textbf{Münkemüller T}, \textbf{McClean C}, \textbf{Osborne PE},
\textbf{Reineking B}, \textbf{Schröder B}, \textbf{Skidmore AK},
\textbf{Zurell D}, \textbf{Lautenbach S}. 2013. Collinearity: A review
of methods to deal with it and a simulation study evaluating their
performance. Ecography \textbf{36}:27--46.
doi:\href{https://doi.org/10.1111/j.1600-0587.2012.07348.x}{10.1111/j.1600-0587.2012.07348.x}.

\hypertarget{ref-kocheturov_massive_2019}{}
33. \textbf{Kocheturov A}, \textbf{Pardalos PM}, \textbf{Karakitsiou A}.
2019. Massive datasets and machine learning for computational
biomedicine: Trends and challenges. Ann Oper Res \textbf{276}:5--34.
doi:\href{https://doi.org/10.1007/s10479-018-2891-2}{10.1007/s10479-018-2891-2}.

\hypertarget{ref-kim_improved_2018}{}
34. \textbf{Kim M}, \textbf{Oh I}, \textbf{Ahn J}. 2018. An improved
method for prediction of cancer prognosis by network learning. Genes
\textbf{9}:478.
doi:\href{https://doi.org/10.3390/genes9100478}{10.3390/genes9100478}.

\hypertarget{ref-sze_leveraging_2018}{}
35. \textbf{Sze MA}, \textbf{Schloss PD}. 2018. Leveraging existing 16S
rRNA gene surveys to identify reproducible biomarkers in individuals
with colorectal tumors. mBio \textbf{9}:e00630--18.
doi:\href{https://doi.org/10.1128/mBio.00630-18}{10.1128/mBio.00630-18}.

\hypertarget{ref-schloss_introducing_2009}{}
36. \textbf{Schloss PD}, \textbf{Westcott SL}, \textbf{Ryabin T},
\textbf{Hall JR}, \textbf{Hartmann M}, \textbf{Hollister EB},
\textbf{Lesniewski RA}, \textbf{Oakley BB}, \textbf{Parks DH},
\textbf{Robinson CJ}, \textbf{Sahl JW}, \textbf{Stres B},
\textbf{Thallinger GG}, \textbf{Van Horn DJ}, \textbf{Weber CF}. 2009.
Introducing mothur: Open-Source, Platform-Independent,
Community-Supported Software for Describing and Comparing Microbial
Communities. ApplEnvironMicrobiol \textbf{75}:7537--7541.

\hypertarget{ref-westcott_opticlust_2017}{}
37. \textbf{Westcott SL}, \textbf{Schloss PD}. 2017. OptiClust, an
Improved Method for Assigning Amplicon-Based Sequence Data to
Operational Taxonomic Units. mSphere \textbf{2}.
doi:\href{https://doi.org/10.1128/mSphereDirect.00073-17}{10.1128/mSphereDirect.00073-17}.

\hypertarget{ref-rognes_vsearch_2016}{}
38. \textbf{Rognes T}, \textbf{Flouri T}, \textbf{Nichols B},
\textbf{Quince C}, \textbf{Mahé F}. 2016. VSEARCH: A versatile open
source tool for metagenomics. PeerJ \textbf{4}:e2584.
doi:\href{https://doi.org/10.7717/peerj.2584}{10.7717/peerj.2584}.

\hypertarget{ref-li_hyperband:_2016}{}
39. \textbf{Li L}, \textbf{Jamieson K}, \textbf{DeSalvo G},
\textbf{Rostamizadeh A}, \textbf{Talwalkar A}. 2016. Hyperband: A novel
bandit-based approach to hyperparameter optimization. arXiv:160306560
{[}cs, stat{]}.
